Z-Resonance at LEP

### 2010-07-27 Z0-Publikation/tex/paper-template.tex
weiter...
update
kleine verbesserungen

The detector for all of these particles is the LEP. It`s structure can be seen
in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector\cite{script}}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes, starting from the
vertex point, these are the tracking chamber, the electromagnetic calorimeter,
the hadronic calorimeter and finally the muon chamber.

In our case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without an important loss of energy, because these are the only particles that
are able to reach there. For further information about the detector design can
be found in \cite{script}.

@@

For a detailed analysis of the mentioned processes it is important to be able
to distinguish between muonic and hadronic decays, we did some Monte Carlo
studies to figure out how these two processes look like. This gave us the
possibility to apply cuts on the measured distributions. In this paper we are
already able to show the results of measurements at center of mass energies at
89.48, 91.33 and \SI{93.02}{\giga\electronvolt}.

\subsection{ Event selection}

@@

\end{thebibliography}
\end{document}

>>>>

The detector for all of these particles is LEP. Its structure can be seen
in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector\cite{script}}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes, starting from the
interaction point, these are the tracking chamber, the electromagnetic calorimeter,
the hadronic calorimeter and finally the muon chamber.

In our case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without a significant loss of energy, because these are the only particles that
are able to reach there. Further information about the detector design can
be found in \cite{script}.

@@

For a detailed analysis of the mentioned processes it is important to be able
to distinguish between muonic and hadronic decays. We did some Monte Carlo
studies to figure out how these two processes look like. This gave us the
possibility to apply cuts on the measured distributions. In this paper we are
already able to show the results of measurements at center of mass energies of
89.48, 91.33 and \SI{93.02}{\giga\electronvolt}.

\subsection{ Event selection}
Muons barely interact with any matter, therefore there are only very few
entries in the calorimeter along the track of the muon. This has an immense
discriminating power, because jets ...

@@

\end{thebibliography}

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{E_vis}
 \caption{Distribution of visible energie}
 \label{fig:e_vis}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{N_Cluster}
 \caption{Distribution of entries in the calorimetre}
 \label{fig:n_cluster}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalhad_fit}
 \caption{Breit-Wigner-Fit hadrons}
 \label{fig:e_vis}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalmu_fit}
 \caption{Breit-Wigner-Fit muons}
 \label{fig:n_cluster}
\end{figure}

\end{document}
